Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Note abbreviations in table description
AV condition description

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% assumption
We assumed that different categories would - on average - depict different
stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial layout within a setting (\texttt{vpe\_new})
at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to an already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
When the spatial layout within a setting is already established, shots tend to
more often depict (faces of) persons talking to each others or objects more
relevant to the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

>>>>

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at the beginning of a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

As a control condition with events of no particular processing of spatial
information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
continuous movie shots that lasted longer than \unit[20]{s}, and
% no cuts: how
had a minimum temporal distance of at least \unit[10]{s} to any movie cut and
to any other \texttt{no\_cut} event.
